### 2024-01-17 docs/projects/visual-tools/clay-calva-demo-20231216/index.qmd
rerendered

---
<style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="https://cdn.datatables.net/1.13.6/js/jquery.dataTables.min.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script><link href="https://cdn.datatables.net/1.13.6/css/jquery.dataTables.min.css" rel="stylesheet" type="text/css" />
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>

@@

<div class="sourceClojure">
```clojure
(ns index
  (:require [scicloj.noj.v1.datasets
             :as datasets]
            [scicloj.noj.v1.vis.hanami
             :as hanami]
            [scicloj.kindly.v4.kind
             :as kind]))
```
</div>

@@

<div class="sourceClojure">
```clojure
(+ 1 2)
```
</div>

<div class="printedClojure">
```clojure
3

```
</div>

@@

<div class="sourceClojure">
```clojure
datasets/iris
```
</div>

@@

<div class="sourceClojure">
```clojure
(-> datasets/iris
    kind/table)
```
</div>

>>>>

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="index_files/md-default1.js" type="text/javascript"></script><script src="index_files/md-default2.js" type="text/javascript"></script><script src="index_files/vega3.js" type="text/javascript"></script><script src="index_files/vega4.js" type="text/javascript"></script><script src="index_files/vega5.js" type="text/javascript"></script>
<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>

@@

::: {.sourceClojure}
```clojure
(ns index
  (:require [scicloj.noj.v1.datasets
             :as datasets]
            [scicloj.noj.v1.vis.hanami
             :as hanami]
            [scicloj.kindly.v4.kind
             :as kind]))
```
:::

::: {.sourceClojure}
```clojure
(kind/video {:youtube-id "X_SsjhmG5Ok"})
```
:::

<div style="max-height:600px;overflow-y:auto;"><iframe allowfullscreen="allowfullscreen" src="https://www.youtube.com/embed/X_SsjhmG5Ok"></iframe></div>

@@

::: {.sourceClojure}
```clojure
(+ 1 2)
```
:::

::: {.printedClojure}
```clojure
3

```
:::

@@

::: {.sourceClojure}
```clojure
datasets/iris
```
:::

@@

::: {.sourceClojure}
```clojure
(-> datasets/iris
    kind/table)
```
:::

<div style="max-height:600px;overflow-y:auto;"><table class="table"><thead><tr><th>sepal-length</th><th>sepal-width</th><th>petal-length</th><th>petal-width</th><th>species</th></tr></thead><tbody><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.3</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.0</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.7</p></div></td><td><div><p>0.5</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.7</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.1</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.4</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.6</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.9</p></div></td><td><div><p>0.4</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.3</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>4.6</p></div></td><td><div><p>3.2</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.3</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.4</p></div></td><td><div><p>0.2</p></div></td><td><div><p>setosa</p></div></td></tr><tr><td><div><p>7.0</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.2</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.9</p></div></td><td><div><p>3.6</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.2</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.7</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>3.5</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.8</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.4</p></div></td><td><div><p>3.7</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>3.9</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.4</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.4</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.6</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>4.7</p></div></td><td><div><p>1.5</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.5</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.4</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.6</p></div></td><td><div><p>4.0</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.0</p></div></td><td><div><p>2.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>1.0</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.2</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.2</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.9</p></div></td><td><div><p>4.3</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>1.1</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.1</p></div></td><td><div><p>1.3</p></div></td><td><div><p>versicolor</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.3</p></div></td><td><div><p>6.0</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.6</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>4.9</p></div></td><td><div><p>2.5</p></div></td><td><div><p>4.5</p></div></td><td><div><p>1.7</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.3</p></div></td><td><div><p>2.9</p></div></td><td><div><p>6.3</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.6</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.3</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.3</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.6</p></div></td><td><div><p>6.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>2.2</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.6</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.9</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.7</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.7</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.2</p></div></td><td><div><p>6.0</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>2.8</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.9</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.2</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.8</p></div></td><td><div><p>1.6</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>6.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.9</p></div></td><td><div><p>3.8</p></div></td><td><div><p>6.4</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.2</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.8</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.1</p></div></td><td><div><p>2.6</p></div></td><td><div><p>5.6</p></div></td><td><div><p>1.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>7.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>6.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.4</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.5</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.0</p></div></td><td><div><p>3.0</p></div></td><td><div><p>4.8</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.1</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.6</p></div></td><td><div><p>2.4</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.9</p></div></td><td><div><p>3.1</p></div></td><td><div><p>5.1</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.8</p></div></td><td><div><p>2.7</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.8</p></div></td><td><div><p>3.2</p></div></td><td><div><p>5.9</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.3</p></div></td><td><div><p>5.7</p></div></td><td><div><p>2.5</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.7</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.3</p></div></td><td><div><p>2.5</p></div></td><td><div><p>5.0</p></div></td><td><div><p>1.9</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.5</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.2</p></div></td><td><div><p>2.0</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>6.2</p></div></td><td><div><p>3.4</p></div></td><td><div><p>5.4</p></div></td><td><div><p>2.3</p></div></td><td><div><p>virginica</p></div></td></tr><tr><td><div><p>5.9</p></div></td><td><div><p>3.0</p></div></td><td><div><p>5.1</p></div></td><td><div><p>1.8</p></div></td><td><div><p>virginica</p></div></td></tr></tbody></table></div>
